Declarative Integration of Interactive 3D Graphics into the World-Wide Web:\\Principles, Current Approaches, and Research Agenda

### 2013-04-23 Web3D2013-Dec3D/paper.tex
switched to final mode

\documentclass[review]{acmsiggraph}

@@

%\title{A Polyfill Approach to Declarative Integration of Interactive 3D Graphics\\ into the World-Wide Web}
\title{Declarative Integration of Interactive 3D Graphics into the World-Wide Web:\\Principles, Current Approaches, and Research Agenda
\\~} %some space that we don't get over 4(?) pages in the final version

\author{Name Lastname\thanks{e-mail:name.lastname@someemail.com}\\Some Research Institution}
\pdfauthor{Name Lastname}

@@

\keywordlist
\copyrightspace

@@

XML3D \cite{Sons2010} is a collaboration of DFKI and Intel VCI. Similar to X3DOM, it employs CSS3, DOM scripting, DOM events, and WebGL. In contrast to X3DOM, XML3D is designed as a extension to HTML5 from scratch. It does not define a scene-graph but uses the DOM tree structure for parent child relations and second level references e.g\ via CSS to (re-)use resources such as geometry data, material descriptions or animation data. These resources are not necessarily in the same document, but can also come from external documents in various formats, e.g. as JSON files.

>>>>

\documentclass{acmsiggraph}
%\documentclass[review]{acmsiggraph}

@@

\setlength{\ACMcopyrightspace}{1.0in}

%\title{A Polyfill Approach to Declarative Integration of Interactive 3D Graphics\\ into the World-Wide Web}
\title{Declarative Integration of Interactive 3D Graphics into the World-Wide Web:\\Principles, Current Approaches, and Research Agenda}

\author{
Jacek Jankowski\thanks{e-mail:jacek.jankowski@inria.fr} \\ INRIA \\ Bordeaux \\ France
\and Sandy Ressler\thanks{e-mail:sandynist@gmail.com} \\ NIST \\ Gaithersburg MD \\ USA
\and Kristian Sons\thanks{e-mail:kristian.sons@dfki.de} \\ DFKI GmbH \\ Saarbr\"ucken \\ Germany
\and Yvonne Jung\thanks{e-mail:yvonne.jung@igd.fraunhofer.de} \\ Fraunhofer IGD \\ Darmstadt \\ Germany
\and Johannes Behr\thanks{e-mail:johannes.behr@igd.fraunhofer.de} \\ Fraunhofer IGD \\ Darmstadt \\ Germany
\and Philipp Slusallek\thanks{e-mail:slusallek@cs.uni-saarland.de} \\ DFKI GmbH \& Universit\"at des Saarlandes \\ Saarbr\"ucken \\ Germany
}

\pdfauthor{Jacek Jankowski, Sandy Ressler, Kristian Sons, Yvonne Jung, Johannes Behr, Philipp Slusallek}

@@

\keywordlist

\copyrightspace

@@

It is also worth mentioning that the Web applications shown in Figures \ref{fig:chApps} and \ref{fig:cadApps} were not realized by graphics programmers but mainly by Web developers, using standard DOM scripting as well as JavaScript frameworks like jQuery \cite{jquery}. For example, to switch to a certain viewpoint when the user clicks onto the arrow button in the walkthrough application shown in Figure \ref{fig:chApps} (left), the application developer simply needs to update the 'bind' attribute of the "viewpoint" tag by calling its \emph{setAttribute} method.

XML3D \cite{Sons2010} is a collaboration of DFKI and Intel VCI. Similar to X3DOM, it employs CSS3, DOM scripting, DOM events, and WebGL. In contrast to X3DOM, XML3D is designed as a extension to HTML5 from scratch. It does not define a scene-graph but uses the DOM tree structure for parent child relations and second level references e.g\ via CSS to (re-)use resources such as geometry data, material descriptions or animation data. These resources are not necessarily in the same document, but can also come from external documents in various formats, e.g. as JSON. % files.
